An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-07 poly-embed-journal/poly-embed-journal.tex
Re-defining trim

\jessie{Adding new statements}
\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
	Construct the set $\Sc(L)$ as follows:
	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
\end{definition}

\begin{proposition}
	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	First, we have to show that $\Sc(L)$ is a representative set.
	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.

	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
	By the construction of $\Sc$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, so these are equal.
	By construction of $\Sc$, we must have only added at most one of these to the set.
	Therefore, $\Sc(L)$ is a minimal representative set.
\end{proof}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral.%; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\raf{Some thoughts on this section:
  \begin{itemize}
  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
    \begin{itemize}
    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
    \end{itemize}
  \end{itemize}}

@@

@@

\btw{JESSIE: Figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$ and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
	% in one of two cases:
	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$. Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

@@

	1 $\Rightarrow$ 2:
	%\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
	If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
	\raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
	By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
	As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
	%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$.\jessie{Needs more/different justification, since we union over $\Sc$ instead of $\R$ }

>>>>

\jessie{Adding new statements}
\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
	Construct the set $\Sc(L)$ as follows:
	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
\end{definition}

\begin{proposition}\label{prop:SL-minimal}
	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	First, we have to show that $\Sc(L)$ is a representative set.
	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.

	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc(L)$ such that $\Sc' := \Sc(L) \setminus \{s\}$ is also a representative set for $L$.
	By the construction of $\Sc(L)$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
	By construction of $\Sc$, we must have only added at most one of these to the set.
	Therefore, $\Sc(L)$ is a minimal representative set.
\end{proof}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\raf{Some thoughts on this section:
  \begin{itemize}
  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
    \begin{itemize}
    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
    \end{itemize}
  \end{itemize}}

@@

\begin{definition}\label{def:trim}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\jessie{Do we want to re-define $\trim(\Gamma) = \{\Gamma_r \mid r \in \Sc\}$ for any minimal representative set $\Sc$?}

@@

\btw{JESSIE: Figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimal representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
	% in one of two cases:
	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimal representative set}, which is a minimal representative set by Proposition~\ref{prop:SL-minimal}. 
	Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

@@

	1 $\Rightarrow$ 2:
	%\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
	If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
	\raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
	By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
	As $\R$, and therefore $\Sc$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
	%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
	Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$, since if this were not true, $\Sc$ would not be a representative set for $\gamma$.
